---
title: "Talian"
bibliography: talian/ref_talian.bib
csl: talian/apa.csl
output:
  html_document:
    df_print: paged
---



<style>
.image {
  border-radius: 50%;
  <!-- margin: 0.5rem; -->
  min-width: 50%;
  opacity: 1;
  display: block;
  width: 100%;
  height: auto;
  transition: .5s ease;
  backface-visibility: hidden;
}

.curve { 
	width: 35%;
	max-width: 100%;
	height: auto;
	float: right;
	margin: 1.5rem;
	margin-right:1rem;
	shape-outside:circle(50%);
	-webkit-clip-path: circle(50%);
}

<!-- .container { -->
<!--   position: relative; -->
<!--   width: 100%; -->
<!-- } -->

<!-- .middle { -->
<!--   transition: .5s ease; -->
<!--   opacity: 0; -->
<!--   position: absolute; -->
<!--   top: 50%; -->
<!--   left: 50%; -->
<!--   transform: translate(-50%, -50%); -->
<!--   -ms-transform: translate(-50%, -50%) -->
<!-- } -->

<!-- .container:hover .image { -->
<!--   opacity: 0.3; -->
<!-- } -->

<!-- .container:hover .middle { -->
<!--   opacity: 1; -->
<!-- } -->

<!-- .text { -->
<!--   <!-- background-color: white; --> -->
<!--   color: white; -->
<!--   text-color: white; -->
<!--   font-size: 16px; -->
<!--   padding: 6px 6px; -->
<!-- } -->
</style>



<div align = "justify">


`Under construction.` Project by: <a href = "https://nataliaguzzo.github.io" target = "_blank">**Natália B. Guzzo**</a> and <a href="https://guilhermegarcia.github.io" target = "_blank">**Guilherme D. Garcia**</a>

<div class = "curve"><img src = "talian/photos/AP/house3.jpg" class = "image" alt = "Antônio Prado, Rio Grande do Sul"></div>In the 19th century, Italian immigrants moved to North and South America. In Brazil, they first immigrated to the southeastern region, and subsequently to the southern region---especially to the southernmost state in the country, <a href = "https://en.wikipedia.org/wiki/Rio_Grande_do_Sul" target = "_blank">Rio Grande do Sul</a>. Many of these immigrants were speakers of <a href = "https://en.wikipedia.org/wiki/Venetian_language" target = "_blank">Veneto</a>, a Romance language spoken in northern Italy. As time went by, a dialect of Veneto, *Brazilian Veneto*, developed in the area(s) where the immigrants settled---we refer to this dialect as *Talian*. In total, there are approximately 500,000 speakers of Talian in Brazil---with varying degrees of proficiency.

We are currently working on a written corpus of Talian, which will be made available here in the near future. Our project focuses on the Talian spoken in the *Italian Immigration Area* (IIA), the area of Rio Grande do Sul where Italian immigrants first settled. The picture shows a historic house in the IIA town of <a href = "https://en.wikipedia.org/wiki/Antônio_Prado" target = "_blank">**Antônio Prado**</a>, where we can find numerous speakers of Talian. 


---



<h3>The Italian Immigration Area in Brazil</h3>

The towns and cities in red have Talian as their co-official language, alongside (Brazilian) Portuguese. The gray circle is an approximation representing the Italian Immigration Area in the state of Rio Grande do Sul.

<div align = "center">

```{r, echo = TRUE, fig.align='center', echo = FALSE, message=FALSE, warning=FALSE}
library(leaflet)
library(tidyverse)

# 3, 6 zoom
iia = read_csv("talian/IIA_map.csv")

leaflet(data = iia, width = "80%", height = 600, 
        options = leafletOptions(minZoom = 3, maxZoom = 10, zoomControl = TRUE)) %>% 
    addProviderTiles("OpenStreetMap.Mapnik") %>%
    addCircles(lat = -28.95, lng = -51.54, 
               radius = 55000, color = "Black") %>% 
    setView(zoom = 6, lat = -28.9, lng = -51.542461) %>% 
    addCircleMarkers(lng = iia$long, lat = iia$lat, stroke = F, 
                     radius = log(iia$pop),
                     color = "FireBrick", fillOpacity = 0.5,
                     label = str_c(iia$address, 
                                   " (Pop: ", format(round(as.numeric(iia$pop), 1), 
                                                     nsmall=0, big.mark=","), ")")) 


# leaflet(data = iia, width = "80%", height = 400, 
#         options = leafletOptions(minZoom = 5, maxZoom = 10, zoomControl = FALSE)) %>% 
#     addProviderTiles("OpenStreetMap.Mapnik") %>%
#     addCircleMarkers(lng = iia$long, lat = iia$lat, stroke = TRUE, 
#                      color = "Red", fillOpacity = 0.5, radius = 2,
#                      label = iia$address) %>% 
#     addPolylines(data = iia, lng = ~long, lat = ~lat,
#                 fill = T, fillOpacity = 0.3, weight = 0, 
#                 color = "red", smoothFactor = 1)

```

---

</div>

<h3>Our Talian Corpus</h3>



```{r echo = FALSE, warning=FALSE, message=FALSE}
library(kableExtra)
library(knitr)
require(tidyverse)

load(url("http://guilhermegarcia.github.io/talian/corpus/talian.RData"))

```

Our corpus consists of internet texts from the IIA as well as excerpts from books written in Talian. Text processing is being done in R [@r_language], and optical character recognition (OCR) is being carried out using Google's <a href = "https://github.com/tesseract-ocr/tesseract/" target = "_blank">**Tesseract**</a> [@tesseract]. As a starting point, we used trained data from Italian in Tesseract, and later checked for potential mismatches.

<h4>Stage 1: Fall 2020</h4>

- Data collection, OCR, tokenization
    - ``r formatC(nrow(Talian), big.mark = ",")` words (in progress)`
    - ``r formatC(length(levels(Talian$sentence)), big.mark = ",")` sentences (in progress)`
- Initial coding
- Make initial version available

<h4>Stage 2: Spring 2021</h4>

- Phonetic transcription
- Syllabification
- Tagging (part of speech)

<font color = "gray">*Last updated: `r format(Sys.Date(), "%B %d, %Y")`*</font>

---

<h3>What the corpus looks like</h3>

The corpus currently has `r ncol(Talian)` variables/columns. In the table below, you can see a subset of such variables.

```{r kable, echo = FALSE, warning=FALSE, message=FALSE}
set.seed(5)
kable(Talian %>% slice(1:10) %>% 
          select(sentence, wd, sLength, freq, logFreq, author, year, sylls, IPA, nSyll),
      row.names = FALSE, digits = 3) %>%
    kable_styling(full_width = F)

```
<br>

The corpus follows a `tidy data` approach [@wickham2014tidy], so little (if any) data wrangling is needed to analyze the data.


---

<h3><i class="fas fa-cloud-download-alt"></i>&emsp;Download corpus</h3>

To access the corpus, click [**here**](talian_form.html).

---

<h3>References</h3>

<div id="refs"></div>

</div>


---
